Multiplex stream graphs

### 2019-04-24 tex/main.tex
Comestic change for todonotes (for jeff)
ajout d'exemples pour la définition

\newcommand{\tiph}[1]{\todo[inline,color=Orchid]{#1}}
\newcommand{\pimprenelle}[1]{\todo[inline, color=ForestGreen]{#1}}

\title{Multiplex stream graphs}
\author{Pimprenelle Parmentier, Tiphaine Viard, ...}

@@

    \section{Multiplex stream graphs}

	\pimprenelle{Multilayer stream graphs serait peut etre plus général ?}
	\subsection{Definition}
    We define a multiplex stream graph as a tuple $M = (T,T_M,V,W_M,E_M,{\cal L})$, such that $T$ and $V$ are, respectively, a time interval and a set of nodes, just like in stream graphs. 
    As in multilayer graphs, ${\cal L}$ is a set of $d$ {\em aspects}; ${\cal L} = \{L_i\}_{i=1}^d$, and an element $\alpha_i$ of $L_i$ is named {\em elementary layer}. An element of $L=L_1\times \dots \times L_d$ is named {\em layer}. From those elements, $V_M$ is defined as follows : $V_M = \{ (u,\alpha), u\in V, \alpha \in L\}$ .

@@

    \begin{rmq}
    	Note that $V$ can be seen as the aspect $L_0$ with $T_0 = T$ and that more generally it is just an aspect similar to the other ones.
    \end{rmq}

@@

@@

    \nocite{*}
	\bibliography{main}

>>>>

\theoremstyle{remark}
\newtheorem{ex}{Example}

\newcommand{\tiph}[1]{\todo[inline,color=Orchid]{#1}}
\newcommand{\pimprenelle}[1]{\todo[inline, color=ForestGreen]{#1}}
\newcommand{\jeffin}[1]{\todo[inline, color=BrickRed]{#1}}
\newcommand{\jeff}[1]{\todo[color=BrickRed]{#1}}

\title{Multiplex stream graphs}
\author{Pimprenelle Parmentier, Tiphaine Viard, \ldots}

@@

    \section{Multilayer stream graphs}

	\subsection{Definition}
    We define a multiplex stream graph as a tuple $M = (T,T_M,V,W_M,E_M,{\cal L})$, such that $T$ and $V$ are, respectively, a time interval and a set of nodes, just like for stream graphs \cite{stream}.
    As for multilayer graphs \cite{mlkiv}, ${\cal L}$ is a set of $d$ {\em aspects}; ${\cal L} = \{L_i\}_{i=1}^d$, and an element $\alpha_i$ of $L_i$ is named {\em elementary layer}. An element of $L=L_1\times \dots \times L_d$ is named {\em layer}. From those elements, the set of {\em node-layers } $V_M$ is defined as follows : $V_M = \{ (u,\alpha), u\in V, \alpha \in L\}$.

@@

    \pimprenelle{Note that $V$ can be seen as the aspect $L_0$ with $T_0 = T$ and that more generally it is just an aspect similar to the other ones. .... a discuter}

@@

	\pimprenelle{FIGURE + EXEMPLE }

	\begin{ex}[Research world]\label{exresearch}
	We consider a set of people working in research.

	These people can work in one or more universities and/or companies, in one or more departments. They can work together on different ways : they can collaborate on a paper, supervise or being supervised. And their work on different subjects, linked together thanks to keywords.

	The multilayer stream graph is the following :
	\begin{itemize}
		\item the {\bf nodes V} are the researchers
		\item the {\bf aspects L} are : the university/companies , the departments, the subjects, the type of status of interaction (supervisor/ supervised / collaborator) 
		\item {\bf links} appear during an interaction between two researchers.
		\item all these parameters vary with time, the set $T$ is chosen arbitrarily
	\end{itemize}

	Question : which aspect is the more important in the spreading and creation of knowledge ?

	\end{ex}

	\begin{figure}
    	\centering
    	\includegraphics[width=15cm]{schemas/chercheurs.jpg}
    	\caption{An simplified scheme of a multiplex stream graph for example \ref{exresearch}. The nodes are the researchers R1,R2,R3, and the aspects are the Universities (U1,U2,U3), and the department (Maths, Computer sciences, Physics)}
    	\label{fig:chercheurs}
	\end{figure}

	\begin{ex}[Epidemics between species]
		We consider an set of individuals from different species, and a disease. This disease could be transmitted through different types of interaction : by blood, by  by respiratory tracts, digestive tracks, etc.

		The stream-multilayer graph is the following : 
		\begin{itemize}
			\item the {\bf nodes V} are the individuals
			\item the {\bf aspects L} are : the species, the type of possible interaction, the state of the individual (sane, infected, contagious, dead, recoved ... ) 
			\item {\bf links} appear when there is an interaction between two individuals.
			\item all these parameters vary with time, the set $T$ is chosen arbitrarily (from example from the start of the infection)
		\end{itemize}

		The question here could be : when and where do we have to act (cut some connection / remove some node-layer) to stop the spreading of the disease as soon as possible ?
	\end{ex}

	\begin{rmq}
		We notice that it is easy to make the multilayer as complex as we want. Three rules seem to be important to have a pertinent use of multiplex-stream graph :
		\begin{itemize}
			\item a set of nodes which could have various properties which can be "melted"
			\item different ways to interact between the nodes in function of their properties
			\item a time-dependency
		\end{itemize}
	\end{rmq}

@@

    \nocite{*}
    \bibliographystyle{plain}
	\bibliography{main}
